### 2017-04-23 Manuscripts/cog-psych/cogpsych.tex
ready to pass to joe

In our implementation of their model, each category's exemplars are assumed to be sampled from a multivariate Normal distribution with parameters ($\mu, \Sigma$). Each category's covariance matrix is assumed to be inverse-Wishart distributed with parameters: $v$, $\kappa,$ and $\Sigma_D$\footnote{Note that \citet{jern2013probabilistic}'s model is slightly different, as they used a non-conjugate model. Their model acts very similar to our version of it and receives comparable fits.}. $\Sigma_D$ is the covariance matrix shared between categories. We assume the shared covariance matrix $\Sigma_D$ is generated from a Wishart distribution (for conjugacy) with parameters $v_0$, $\kappa_0$, and $\Sigma_0$. We set $\nu_0 = 4$, and $\Sigma_0 = \lambda {\bf I}$, where $\lambda$ is a free parameter controlling the expected variance of dimensions (dimensions of the shared covariance matrix are expected to be uncorrelated) and ${\bf I}$ is the identity matrix.

>>>>

In our implementation of their model, each category's exemplars are assumed to be sampled from a multivariate Normal distribution with parameters ($\mu, \Sigma$). Each category's covariance matrix is assumed to be inverse-Wishart distributed with parameters: $v$, $\kappa,$ and $\Sigma_D$
\footnote{Note that \citet{jern2013probabilistic}'s model is slightly different, as they used a non-conjugate model. Their model acts very similar to our version of it and receives comparable fits.}. 
$\Sigma_D$ is the covariance matrix shared between categories. We assume the shared covariance matrix $\Sigma_D$ is generated from a Wishart distribution (for conjugacy) with parameters $v_0$, $\kappa_0$, and $\Sigma_0$. We set $\nu_0 = 4$, and $\Sigma_0 = \lambda {\bf I}$, where $\lambda$ is a free parameter controlling the expected variance of dimensions (dimensions of the shared covariance matrix are expected to be uncorrelated) and ${\bf I}$ is the identity matrix.
